---
title: "Results Summary"
output: html_document
date: "2024-03-05"
---

This document summarises the results from the project exploring optimal fire age classes under alternative fox baiting intensities. 

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(sf)
library(terra)
library(tidyverse)
library(tidybayes)
library(cowplot)
library(AHMbook)
library(ggridges)
```

# The Data
## Species Data

These plots show the number of independent detections per site just to give a feel for where each species are found in the study region. This is important for understanding the spatial variation in the optimal fire ages later on... 

- Woylies in the north-east
- Numbats in the north-east
- Koomal kind of everywhere
- Chuditch kind of everywhere but a bit in the middle
- Quenda generally in the northern half

```{r echo=FALSE, fig.height=12, fig.width=8, message=FALSE, warning=FALSE, paged.print=FALSE}
load(here::here("Data_Clean", "covariates_stack.RData"))
sites = read_sf("Data_Processing/shapefiles/trap.points.shp")
dethist = readRDS(here::here("Data_Processing","camtrapR.counthist.UpperWarren.multispp09122023.RData"))
base = covariates_masked$base_raster %>% as.data.frame(xy=TRUE) %>% na.omit()

woylie.sites = data.frame(X = dethist$Sites$X, 
                          Y = dethist$Sites$Y,
                          Woylie = rowSums(dethist$Species$Woylie, na.rm=TRUE))
woylie = ggplot() + 
  geom_raster(aes(x=base$x,y=base$y, fill=base$base_raster)) +
  geom_point(aes(x=woylie.sites$X, y=woylie.sites$Y, size = woylie.sites$Woylie)) + guides(fill="none",size = guide_legend(title = "Woylie"))+
  coord_equal()

chuditch.sites = data.frame(X = dethist$Sites$X, 
                          Y = dethist$Sites$Y,
                          Chuditch = rowSums(dethist$Species$Chuditch, na.rm=TRUE))
chuditch = ggplot() + 
  geom_raster(aes(x=base$x,y=base$y, fill=base$base_raster)) +
  geom_point(aes(x=chuditch.sites$X, y=chuditch.sites$Y, size = chuditch.sites$Chuditch)) + guides(fill="none",size = guide_legend(title = "Chuditch"))+
  coord_equal()

numbat.sites = data.frame(X = dethist$Sites$X, 
                          Y = dethist$Sites$Y,
                          numbat = rowSums(dethist$Species$Numbat, na.rm=TRUE))
numbat = ggplot() + 
  geom_raster(aes(x=base$x,y=base$y, fill=base$base_raster)) +
  geom_point(aes(x=numbat.sites$X, y=numbat.sites$Y, size = numbat.sites$numbat)) + guides(fill="none",size = guide_legend(title = "Numbat"))+
  coord_equal()

koomal.sites = data.frame(X = dethist$Sites$X, 
                          Y = dethist$Sites$Y,
                          koomal = rowSums(dethist$Species$Koomal, na.rm=TRUE))
koomal = ggplot() + 
  geom_raster(aes(x=base$x,y=base$y, fill=base$base_raster)) +
  geom_point(aes(x=koomal.sites$X, y=koomal.sites$Y, size = koomal.sites$koomal)) + guides(fill="none",size = guide_legend(title = "Koomal"))+
  coord_equal()

quenda.sites = data.frame(X = dethist$Sites$X, 
                          Y = dethist$Sites$Y,
                          quenda = rowSums(dethist$Species$Quenda, na.rm=TRUE))
quenda = ggplot() + 
  geom_raster(aes(x=base$x,y=base$y, fill=base$base_raster)) +
  geom_point(aes(x=quenda.sites$X, y=quenda.sites$Y, size = quenda.sites$quenda)) + guides(fill="none",size = guide_legend(title = "Quenda"))+
  coord_equal()

cowplot::plot_grid(woylie, chuditch, numbat, koomal, quenda, ncol = 2)

```

## Environmental Data
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
load(here::here("Data_Clean", "covariates_stack.RData"))
#sites = read_sf("Data_Processing/shapefiles/trap.points.shp")
dethist = readRDS(here::here("Data_Processing","camtrapR.counthist.UpperWarren.multispp09122023.RData"))

# Study region
tsf = covariates_masked$tsf_Oct2016 %>% as.data.frame(xy=TRUE) %>% na.omit()
bait = covariates_masked$bait_intensity_2016.10.01_38month_lag %>% as.data.frame(xy=TRUE) %>% na.omit()
sev = covariates_masked$propsev_6yrs_Oct2016_500m %>% as.data.frame(xy=TRUE) %>% na.omit()
rain = covariates_masked$mean_annual_rainfall %>% as.data.frame(xy=TRUE) %>% na.omit()
twi = covariates_masked$topographic_wetness_index %>% as.data.frame(xy=TRUE) %>% na.omit()

# Sampled
tsf.sampled = dethist$Sites$tsf.point
bait.sampled = dethist$Sites$Mean_Intensity_400
sev.sampled = dethist$Sites$PropSevere500
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, fig.width = 12}
## Study Region
tsf_map = ggplot(tsf) + geom_raster(aes(x=x,y=y, fill=tsf_Oct2016)) + 
            scale_fill_viridis_c(name="Time Since Fire") +
            theme_void() +
            theme(legend.position = "bottom") +
  coord_equal()

bait_map = ggplot(bait) + geom_raster(aes(x=x,y=y, fill=bait_intensity_2016.10.01_38month_lag)) + 
  scale_fill_viridis_c(name="Bait Intensity") +
  theme_void() +
  theme(legend.position = "bottom")+
  coord_equal()

sev_map = ggplot(sev) + geom_raster(aes(x=x,y=y, fill=propsev_6yrs_Oct2016_500m)) + 
  scale_fill_viridis_c(name="Proportion Severely Burnt") +
  theme_void() +
  theme(legend.position = "bottom")+
  coord_equal()

rain_map = ggplot(rain) + geom_raster(aes(x=x,y=y, fill=mean_annual_rainfall)) + 
  scale_fill_viridis_c(name="Mean Annual Rainfall") +
  theme_void() +
  theme(legend.position = "bottom")+
  coord_equal()

twi_map = ggplot(twi) + 
  geom_raster(aes(x=x,y=y, fill=topographic_wetness_index)) + 
  scale_fill_viridis_c(name="Topographic Wetness Index") +
  theme_void() +
  theme(legend.position = "bottom")+
  coord_equal()

map.plot = cowplot::plot_grid(tsf_map, sev_map, bait_map,rain_map,twi_map,
                   labels = c("a)", "b)", "c)", "d)", "e)"), ncol=3)
map.plot
```

## Study Sites
What have we actually sampled and how does that compare to the study region more broadly.

### Time Since Fire
We've pretty much sampled the distribution of time since fire variables in the region according to their availability. But that does leave the long-unburnt (>25 years post fire) sites a bit skinny. 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
tsf.hist = ggplot() + 
  geom_density(aes(x = tsf.sampled, fill = 'Sampled'), alpha = 0.4) +
  geom_density(aes(x = tsf$tsf_Oct2016, fill = 'Actual Region'), alpha = 0.4, adjust = 2) +
  scale_fill_manual(values = c('red', 'blue'), 
                    labels = c('Sampled', 'Actual Region')) + xlab('Time Since Fire') +
  labs(fill = "Legend")  # Optional: change the legend title

# Create the intervals using cut() function
tsf.sites = tsf.sampled
intervals <- cut(tsf.sites, breaks = c(0,5,10,15,25, max(tsf.sites)), include.lowest = TRUE)
# Count the occurrences within each interval
tsf.count <- data.frame(table(intervals))

tsf.count = ggplot(tsf.count) + geom_bar(aes(x=intervals, y=Freq), stat='identity') + ylab("Number of Sites")

cowplot::plot_grid(tsf.hist, tsf.count, rel_widths = c(2,1))
```

### Fox baiting intensity
Again, fox baiting has been more or less sampled according to availability. 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Baiting
bait.hist = ggplot() + 
  geom_density(aes(x = bait.sampled, fill = 'Sampled'), alpha = 0.4) +
  geom_density(aes(x = bait$bait_intensity_2016.10.01_38month_lag, fill = 'Actual Region'), alpha = 0.4) +
  scale_fill_manual(values = c('red', 'blue'), 
                    labels = c('Sampled', 'Actual Region')) + xlab('Baiting Intensity') +
  labs(fill = "Legend")  # Optional: change the legend title

# Create the intervals using cut() function
bait.sites = bait.sampled
intervals <- cut(bait.sites, breaks = c(0,50,100, max(bait.sites)), include.lowest = TRUE)
# Count the occurrences within each interval
bait.count <- data.frame(table(intervals))


bait.count = ggplot(bait.count) + geom_bar(aes(x=intervals, y=Freq), stat='identity') + ylab("Number of Sites")

cowplot::plot_grid(bait.hist, bait.count, rel_widths = c(2,1))
```

### Fire Severity
We have probably sampled the lower amounts of fire severity disproportionately, but its not too bad. We still have data cross a range of fire severity values.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Fire Severity
sev.hist = ggplot() + 
  geom_density(aes(x = sev.sampled, fill = 'Sampled'), alpha = 0.4) +
  geom_density(aes(x = sev$propsev_6yrs_Oct2016_500m, fill = 'Actual Region'), alpha = 0.4) +
  scale_fill_manual(values = c('red', 'blue'), 
                    labels = c('Sampled', 'Actual Region')) + xlab('Proportion Burnt Severely') +
  labs(fill = "Legend")  # Optional: change the legend title

# Create the intervals using cut() function
sev.sites = sev.sampled
intervals <- cut(sev.sites, breaks = c(0,0.2,0.5, max(sev.sites)), include.lowest = TRUE)
# Count the occurrences within each interval
sev.count <- data.frame(table(intervals))

sev.count = ggplot(sev.count) + geom_bar(aes(x=intervals, y=Freq), stat='identity') + ylab("Number of Sites")
cowplot::plot_grid(sev.hist, sev.count, rel_widths = c(2,1))

```

# The Abundance Model
## Coefficient Estimates
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dethist = readRDS("Data_Processing/camtrapR.counthist.UpperWarren.multispp09122023.RData")
model_output = readRDS("Data_Clean/nmix_nimblemodel_final.RDS")
model.summary = MCMCvis::MCMCsummary(model_output)
model.summary$.variable = rownames(model.summary)
model.eta.lam = model.summary %>% filter(grepl("eta.lam", .variable)) 
model.eta.lam = model.eta.lam%>%
  mutate(species = as.numeric(str_match(model.eta.lam$.variable, "eta.lam\\[\\s*(\\d+),\\s*(\\d+)\\]")[, 3]))

model.betas = model_output %>% tidy_draws() %>% gather_variables() %>% filter(grepl("beta", .variable))
model.betas = separate(model.betas, .variable, into=c("beta", "species"))

species.predict = c("Chuditch","Quenda", "Woylie", "Vulpes", "Numbat")

nspec=length(species.predict)
spp = species.predict
spp.lookup = data.frame(No = as.character(1:length(species.predict)), Species = species.predict)

model.betas = left_join(model.betas, spp.lookup, by=c("species"="No"))

coef.names = data.frame(beta = c("beta0", "beta1", "beta2", "beta3", "beta4", "beta5", "beta6", "beta7"),
                        Label = c("Intercept", "Mean Annual Rainfall", "TWI", "Baiting", "TSF", "TSF^2", 
                                  "TSF*Baiting", "Fire Severity"))

model.betas = left_join(model.betas, coef.names)

coef.plot = model.betas %>% filter(!Label == "Intercept") %>%
  ggplot() + 
  geom_halfeyeh(aes(y=Label, x=.value, fill=Label)) + 
  geom_vline(xintercept=0, linetype="dashed") +
  facet_wrap(~Species, scales = "free_x") + theme_bw()


# source("Scripts/model_helper_functions.R")
# 
# model.samples=model_output
# spp = c("Chuditch", "Koomal", "Quenda", "Woylie", 
#         "Vulpes", "Numbat")
# nspec = length(spp)
# 
# c.b1 = clean_coefs_90ci("beta1", "Mean Annual Rainfall", spp, model.samples)
# c.b2 = clean_coefs_90ci("beta2", "Topographic Wetness Index", spp, model.samples)
# c.b3 = clean_coefs_90ci("beta3", "Baiting", spp, model.samples)
# c.b4 = clean_coefs_90ci("beta4", "Time Since Fire", spp, model.samples)
# c.b5 = clean_coefs_90ci("beta5", "Time Since Fire^2", spp, model.samples)
# c.b6 = clean_coefs_90ci("beta6", "Time Since Fire * Baiting", spp, model.samples)
# c.b7 = clean_coefs_90ci("beta7", "Fire Severity", spp, model.samples)
# 
# coef.out = rbind(c.b1, c.b2, c.b3, c.b4,c.b5, c.b6, c.b7)
# spplabels= data.frame(Species = spp,
#                       SpeciesLab = c("Chuditch", "Koomal", "Quenda", "Woylie", 
#                                      "Red Fox",  "Numbat"))
# coef.out = left_join(coef.out, spplabels)
# coef.out$SpeciesLab = as.factor(coef.out$SpeciesLab)
# coef.out$SpeciesLab = factor(coef.out$SpeciesLab, levels = rev(levels(coef.out$SpeciesLab)))
# 
# coef.plot = ggplot(coef.out) + 
#   geom_pointrange(aes(x = Covariate, y = Mean, ymin = Lower, ymax = Upper),
#                   shape = ifelse(coef.out$Lower > 0 | coef.out$Upper < 0, 21, 21),
#                   fill = ifelse(coef.out$Lower > 0 | coef.out$Upper < 0, "black", "white")) + 
#   geom_hline(yintercept = 0, linetype='dashed') + ylab("Coeffcient and 90% CIs") + xlab("") +
#   coord_flip() + facet_wrap(~SpeciesLab, ncol=3, scales='free_x') + theme_cowplot()
 coef.plot

```

#### Time Since Fire
- Woylie have a negative relationshiip with Time Since Fire and none with TSF^2. Suggests woylie abundance is highest at younger fuel ages. 
- Quenda have no clear relationship with TSF or TSF^2. 
- Numbat have a very close to clear negative relationship with TSF. Suggests numbat abundance may be trending higher at younger fuel ages. 
- Chuditch have a positive relationship with TSF and a negative relationship with TSF^2. Suggests that 

#### Fox baiting
- Woylie have a positive relationshiip with Fox Baiting intensity. Suggests woylie abundance is highest at high fox baiting intensity. 
- Quenda have no clear relationship with Fox Baiting. 
- Numbat have a positive relationship with Fox Baiting Intensity. Suggests numbat abundance may be trending higher at higher fox baiting intensity. 
- Chuditch have no clear relationship with Fox Baiting.

#### Fire severity
- Woylies have a negative relationship with the amount of habitat burnt severely. 
- Quenda have a negative relationship with the amount of habitat burnt severely. 
- Numbat have a negative relationship with the amount of habitat burnt severely. 
- Chuditch have a negative relationship with the amount of habitat burnt severely. 

#### Time Since Fire x Baiting
- Woylie have a close to clear relationship with an interaction between fox baiting and time since fire. 
- Quenda have a positive relationship with the interaction between fox baiting intensity and time since fire. 
- Numbat have no clear relationship with the interaction between fox baiting intensity and time since fire.  
- Chuditch have no clear relationship with the interaction between fox baiting intensity and time since fire. 

## Abundance Predictions
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12, fig.width = 8}
### Pred Alone
model.coefs = model_output %>%
  tidy_draws() %>%
  gather_variables() %>%
  filter(grepl("beta",.variable)) %>%
  group_by(.variable) %>% 
  summarise(Mean = mean(.value), 
            Lower_10 = quantile(.value, probs = 0.1),
            Upper_90 = quantile(.value, probs = 0.9),
            Lower_5 = quantile(.value, probs = 0.05),
            Upper_95 = quantile(.value, probs = 0.95),
            Lower_2.5 = quantile(.value, probs = 0.025), 
            Upper_97.5 = quantile(.value, probs = 0.975)) %>%
  tidyr::separate(.variable, into=c("coef", "Spp")) %>%
  left_join(spp.lookup, by = c("Spp"="No")) 

bait.pred = seq(from = min(dethist$Sites$Mean_Intensity_400), to = max(dethist$Sites$Mean_Intensity_400), length.out = 100)
bait.pred.std = standardize2match(bait.pred, dethist$Sites$Mean_Intensity_400)
names(bait.pred.std) <- "Bait"

spp.lookup = data.frame(No = as.character(1:length(species.predict)), Species = species.predict)

pred.out = list()
for(i in 1:nspec){ # Loop over each observed species
  coefs = filter(model.coefs, Spp == as.character(i))
  pred.df = data.frame(
    Species = spp[i],
    Bait = bait.pred, 
    Mean = exp(filter(coefs, coef=="beta0")$Mean + 
                 filter(coefs, coef=="beta3")$Mean * bait.pred.std), # Mean
    LCI = exp(filter(coefs, coef=="beta0")$Lower_10 + 
                filter(coefs, coef=="beta3")$Lower_10 * bait.pred.std), # LCI
    UCI = exp(filter(coefs, coef=="beta0")$Upper_90 + 
                filter(coefs, coef=="beta3")$Upper_90 * bait.pred.std) # UCI
  )
  pred.out[[i]]<- pred.df
}

bait.pred.out = do.call('rbind', pred.out)

spplabels= data.frame(Species = species.predict,
                      SpeciesLab = c("Chuditch","Quenda", "Woylie", "Vulpes", "Numbat"))
bait.pred.out = left_join(bait.pred.out, spplabels)

bait.abundance.plot = ggplot(bait.pred.out) + 
  geom_line(aes(x = Bait, y = Mean)) + 
  geom_ribbon(aes(x = Bait, ymin=LCI, ymax=UCI), alpha=0.4) +
  ylab("Predicted Abundance") + xlab("Baits / km^2") + theme_cowplot() + 
  facet_wrap(~SpeciesLab, scales="free_y", nrow=2)

### TSF Alone
tsf.pred = seq(from = min(dethist$Sites$tsf.point), to = max(dethist$Sites$tsf.point), length.out = 100)
tsf.pred.std = standardize2match(tsf.pred, dethist$Sites$tsf.point)
spp.lookup = data.frame(No = as.character(1:length(species.predict)), Species = species.predict)
names(tsf.pred.std) <- "TSF"

pred.out = list()
for(i in 1:nspec){ # Loop over each observed species
  coefs = filter(model.coefs, Spp == as.character(i))
  pred.df = data.frame(
    Species = spp[i],
    TSF = tsf.pred,
    Mean = exp(filter(coefs, coef=="beta0")$Mean + 
                 filter(coefs, coef=="beta4")$Mean * tsf.pred.std + 
                 filter(coefs, coef=="beta5")$Mean * tsf.pred.std^2), # Mean
    LCI = exp(filter(coefs, coef=="beta0")$Lower_10 + 
                filter(coefs, coef=="beta4")$Lower_10 * tsf.pred.std + 
                filter(coefs, coef=="beta5")$Lower_10 * tsf.pred.std^2), # LCI
    UCI = exp(filter(coefs, coef=="beta0")$Upper_90 + 
                filter(coefs, coef=="beta4")$Upper_90 * tsf.pred.std + 
                filter(coefs, coef=="beta5")$Upper_90 * tsf.pred.std^2) # UCI
  )
  pred.out[[i]]<- pred.df
}

tsf.pred.out = do.call('rbind', pred.out)

tsf.pred.out= left_join(tsf.pred.out, spplabels)

tsf.abundance.plot = ggplot(tsf.pred.out) + 
  geom_line(aes(x = TSF, y = Mean)) + 
  geom_ribbon(aes(x = TSF, ymin=LCI, ymax=UCI), alpha=0.4) +
  ylab("Predicted Abundance") + xlab("Time Since Fire") + theme_cowplot() + 
  facet_wrap(~SpeciesLab, scales="free_y", nrow=2)

### Pred time since fire
tsf.pred = seq(from = min(dethist$Sites$tsf.point), to = max(dethist$Sites$tsf.point), length.out = 100)
tsf.pred.std = standardize2match(tsf.pred, dethist$Sites$tsf.point)
bait.pred = seq(from = min(dethist$Sites$Mean_Intensity_400), to = max(dethist$Sites$Mean_Intensity_400), length.out = 100)
bait.pred.std = standardize2match(bait.pred, dethist$Sites$Mean_Intensity_400)
pred.grid = expand.grid(tsf.pred, bait.pred); names(pred.grid) <-c("TSF", "Bait")
pred.grid.std = expand.grid(tsf.pred.std, bait.pred.std); names(pred.grid.std) <-c("TSF", "Bait")

spp.lookup = data.frame(No = as.character(1:length(species.predict)), Species = species.predict)

pred.out = list()
for(i in 1:nspec){ # Loop over each observed species
  coefs = filter(model.coefs, Spp == as.character(i))
  pred.df = data.frame(
    Species = spp[i],
    TSF = pred.grid$TSF,
    Bait = pred.grid$Bait, 
    Mean = exp(filter(coefs, coef=="beta0")$Mean + 
                 filter(coefs, coef=="beta4")$Mean * pred.grid.std$TSF + 
                 filter(coefs, coef=="beta5")$Mean * pred.grid.std$TSF^2 + 
                 filter(coefs, coef=="beta3")$Mean * pred.grid.std$Bait + 
                 filter(coefs, coef=="beta6")$Mean * pred.grid.std$Bait * pred.grid.std$TSF), # Mean
    LCI = exp(filter(coefs, coef=="beta0")$Lower_10 + 
                filter(coefs, coef=="beta4")$Lower_10 * pred.grid.std$TSF + 
                filter(coefs, coef=="beta5")$Lower_10 * pred.grid.std$TSF^2 + 
                filter(coefs, coef=="beta3")$Lower_10 * pred.grid.std$Bait + 
                filter(coefs, coef=="beta6")$Lower_10 * pred.grid.std$Bait * pred.grid.std$TSF), # LCI
    UCI = exp(filter(coefs, coef=="beta0")$Upper_90 + 
                filter(coefs, coef=="beta4")$Upper_90 * pred.grid.std$TSF + 
                filter(coefs, coef=="beta5")$Upper_90 * pred.grid.std$TSF^2 + 
                filter(coefs, coef=="beta3")$Upper_90 * pred.grid.std$Bait + 
                filter(coefs, coef=="beta6")$Upper_90 * pred.grid.std$Bait * pred.grid.std$TSF) # UCI
  )
  pred.out[[i]]<- pred.df
}

pred.out = do.call('rbind', pred.out)
pred.out$BaitF = as.factor(round(pred.out$Bait, 2))
pred.out.sub = filter(pred.out, pred.out$BaitF %in% c("4.91","80.07", "120.16"))

pred.out.sub = left_join(pred.out.sub, spplabels)

abundance.plot = ggplot(pred.out.sub) + 
  geom_line(aes(x = TSF, y = Mean, colour = BaitF)) + 
  geom_ribbon(aes(x = TSF, ymin=LCI, ymax=UCI, fill = BaitF), alpha=0.4) +
  ylab("Predicted Abundance") + xlab("Time Since Fire") + labs(colour = "Baits / km^2", fill= "Baits / km^2") +
  scale_fill_viridis_d(labels=c("4","80","120")) + scale_colour_viridis_d(labels=c("4","80","120")) + theme_cowplot() + 
  theme(legend.position="bottom") +
  facet_wrap(~SpeciesLab, scales="free_y", nrow=2)

abundance.plots = plot_grid(bait.abundance.plot, tsf.abundance.plot, abundance.plot, 
                            labels = c("a)", "b)", "c)"), nrow=3)

abundance.plots
```

# The Optimisation
## Scenario Development
Objective: Find the time since fire distributions that maximise the abundance for Woylie, Quenda, Numbat and Chuditch under different combinations of fire severity and baiting intensities. So, for each scenario, we hold baiting and severity constant and predict the abundance of each species under a range of time since fires (0-33 years post-fire), then put it into the optimisation analysis. I tried to pick values that are representative of the current distribution of values in the region. We can discuss this and whether we've got the right balance however. 

Our baiting values are below. These are representative of how different parts of the landscape are currently treated:

- 5 baits per km^2
- 59 baits per km^2 (equivalent to quarterly aerial baiting only)
- 150 baits per km^2 (equivalent to quarterly arial baiting plus monthly ground baiting)

Our fire severity values are below. Per the plots at the start of this document, all of these are within the range of values that have been recorded at particular transects. However, how that scale's up to a regional level is something we should discuss. 

- 0.2 (20% of landscape burnt severely in past 6 years)
- 0.5 (50% of landscape burnt severely in past 6 years)
- 0.8 (80% of landscape burnt severely in past 6 years)

## Optimal Fire Age Distribution
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, , fig.height=8, fig.width =12}
fireage_props_plot = function(data){
  plot.quantiles = data %>% drop_na() %>% 
    group_by(Scenario, .id, TSFCAT) %>% summarise(cost = sum(n)) %>%
    mutate(TSFCAT = factor(TSFCAT, levels = c("0-5 years", "6-10 years", "11-15 years", "16-24 years", ">24 years")),
           Scenario = as.factor(Scenario)) %>%
    mutate(ScenarioLab = case_when(grepl("bL_", Scenario) ~ "Low",grepl("bA_", Scenario) ~ "Medium",
                                   grepl("bAG_", Scenario) ~ "High", TRUE ~ NA_character_)) %>%
    mutate(ScenarioLabF = factor(ScenarioLab, levels = c("Low", "Medium", "High"))) %>%
    group_by(ScenarioLabF,TSFCAT) %>% summarise(Median = quantile(cost, probs=0.5),
                                            Mean = mean(cost),
                                            LCI = quantile(cost, probs=0.1),
                                            UCI = quantile(cost, probs=0.90))
  
  plot.data = data %>% drop_na() %>% 
    group_by(Scenario, .id, TSFCAT) %>% summarise(cost = sum(n)) %>%
    mutate(ScenarioLab = case_when(grepl("bL_", Scenario) ~ "Low",grepl("bA_", Scenario) ~ "Medium",
      grepl("bAG_", Scenario) ~ "High",TRUE ~ NA_character_)) %>%
    mutate(TSFCAT = factor(TSFCAT, levels = c("0-5 years", "6-10 years", "11-15 years", "16-24 years", ">24 years"))) %>%
    mutate(ScenarioLabF = factor(ScenarioLab, levels = c("Low", "Medium", "High"))) 
    plot.out = ggplot(plot.data) + 
    geom_jitter(aes(x=TSFCAT,y=cost/11, colour= TSFCAT), alpha=0.4) + scale_color_viridis_d() + 
    geom_pointrange(data = plot.quantiles, 
                   aes(x=TSFCAT, 
                       y=Mean/11, 
                        ymin=LCI/11, 
                        ymax=UCI/11)) +
    theme_cowplot() + facet_wrap(.~ScenarioLabF, nrow=3) +
    theme(legend.position="none") +
    ylab("Proportion of Landscape") + xlab("Time Since Fire Category")
  return(plot.out)
}

abundance_plot = function(plot.data){
  abundance.plot.quantiles = plot.data %>% 
    filter(summary=="overall") %>%
    mutate(ScenarioLab = case_when(grepl("bL_", Scenario) ~ "Low",grepl("bA_", Scenario) ~ "Medium",
                                   grepl("bAG_", Scenario) ~ "High",TRUE ~ NA_character_)) %>%
    group_by(ScenarioLab, Species) %>% summarise(Median = quantile(absolute_held, probs=0.5),
                                                 Mean = mean(absolute_held),
                                                 LCI = quantile(absolute_held, probs=0.1),
                                                 UCI = quantile(absolute_held, probs=0.9))
  
  woylie_uci = max(abundance.plot.quantiles$UCI[which(abundance.plot.quantiles$Species=="Woylie")])
  quenda_uci = max(abundance.plot.quantiles$UCI[which(abundance.plot.quantiles$Species=="Quenda")])
  numbat_uci = max(abundance.plot.quantiles$UCI[which(abundance.plot.quantiles$Species=="Numbat")])
  chuditch_uci = max(abundance.plot.quantiles$UCI[which(abundance.plot.quantiles$Species=="Chuditch")])
  
  abundance.plot = plot.data %>% filter(summary=="overall") %>%
    mutate(ScenarioLab = case_when(grepl("bL_", Scenario) ~ "Low",grepl("bA_", Scenario) ~ "Medium",
                                   grepl("bAG_", Scenario) ~ "High",TRUE ~ NA_character_)) %>%
    mutate(ScenarioLab = factor(ScenarioLab, levels = c("Low", "Medium", "High"))) %>%
    filter(Species == "Woylie" & absolute_held < woylie_uci | 
             Species == "Quenda" & absolute_held < quenda_uci | 
             Species == "Numbat" & absolute_held < numbat_uci | 
             Species == "Chuditch" & absolute_held < chuditch_uci) %>%
    ggplot() +
    geom_density_ridges(aes(y=ScenarioLab, x = absolute_held, fill=ScenarioLab),
                        alpha=0.8, scale=1.5) + 
    geom_pointrange(data = abundance.plot.quantiles, 
                    aes(y=ScenarioLab, 
                        x=Median, 
                        xmin=LCI, 
                        xmax=UCI)) +
    facet_wrap(~Species, nrow=1, scales="free_x") +
    theme_ridges(grid = FALSE, center_axis_labels = TRUE) + scale_fill_viridis_d(begin=0.2) + 
    xlab("Abundance") + ylab("") + theme(legend.position="none")
  return(abundance.plot)
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, , fig.height=8, fig.width =12}
#### Step 3a: High severity plots only
results.paths = intersect(list.files(path = "Data_Clean", pattern = "baitfireoptimisationresults_transectscale_summaries_s", full = TRUE),
                          list.files(path = "Data_Clean", pattern = "_sH", full = TRUE))
results.paths = results.paths[2:4]

highsev.summaries.out = data.frame()
for (i in seq_along(results.paths)){
  t = read.csv(results.paths[i])
  highsev.summaries.out = rbind(highsev.summaries.out, t)
}

highsev.plot = fireage_props_plot(highsev.summaries.out)

#### Step 3b: Low Severity Plots ####
results.paths = intersect(list.files(path = "Data_Clean", pattern = "baitfireoptimisationresults_transectscale_summaries_s", full = TRUE),
                          list.files(path = "Data_Clean", pattern = "_sL", full = TRUE))
results.paths = results.paths[2:4]

lowsev.summaries.out = data.frame()
for (i in seq_along(results.paths)){
  t = read.csv(results.paths[i])
  lowsev.summaries.out = rbind(lowsev.summaries.out, t)
}

lowsev.plot = fireage_props_plot(lowsev.summaries.out)

#### Step 3c: Medium Severity Plots ####
results.paths = intersect(list.files(path = "Data_Clean", pattern = "baitfireoptimisationresults_transectscale_summaries_s", full = TRUE),
                          list.files(path = "Data_Clean", pattern = "_sM", full = TRUE))
results.paths = results.paths[2:4]

medsev.summaries.out = data.frame()
for (i in seq_along(results.paths)){
  t = read.csv(results.paths[i])
  medsev.summaries.out = rbind(medsev.summaries.out, t)
}

medsev.plot = fireage_props_plot(medsev.summaries.out)

allplot = cowplot::plot_grid(lowsev.plot, medsev.plot, highsev.plot, labels = c("a)", "b)", "c)"), nrow=1)
allplot
```
This set of figures shows us the outcomes of the optimisation -- the distribution of fire ages on the x-axis and their relative proportion in the landscape on the y axes. The vertical Low/Medium/High illustrate teh differences under each fox baiting scenario, and then the figure on the left is for the high fire severity scenario (0.8 of the landscape burnt severely) and the right is for the low fire severity scenario (0.2 of the landscape burnt severely). 

The figures suggest that:

- The optimal proportion of the landscape that is >24 years post-fire increases with increasing baiting intensity (Low, Medium, High)
- The optimal fire age distributions don't really differ when the amount of the landscape burnt severely is varied (0.2 vs. 0.8)

In terms of the species preferences, this kind of makes sense. If we look back to the figure earlier in the document of the model predictions.  

- Woylie and Numbat abundance is higher in younger fuel ages
- Quenda don't really have a preference, but potentially higher in older (uncertainty)
- Chuditch have the hump relationship - like the middle ages (5-15 years post-fire)  but potential for higher in older (uncertainty)

*Importantly, each of these trends are stronger/more pronounced under higher baiting intensities, likely leading to the optimisation results that we're seeing*

## Abundance outcomes

As expected, the scenarios with higher fox baiting intensity lead to higher abundances for woylie, numbat and quenda. Per the model coefficients. 
So, essentially what this is saying is that to increase abundance of each species we have a lever we can pull around fire age distributions, we have a lever we can pull around fox baiting intensity, and it's a bit hard to see in this plot, but there's a lever we can pull around fire severity. 

```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, paged.print=FALSE}
# High Severity 
results.paths = intersect(list.files(path = "Data_Clean", pattern = "baitfireoptimisationresults_transectscale_abundances_s", full = TRUE),
                          list.files(path = "Data_Clean", pattern = "_sH", full = TRUE))
results.paths = results.paths[2:4]

highsev.abundances.out = data.frame()
for (i in seq_along(results.paths)){
  t = read.csv(results.paths[i])
  highsev.abundances.out = rbind(highsev.abundances.out, t)
}

highsev.plot = abundance_plot(highsev.abundances.out)

#### Step 4b: Medium severity abundance plots only 
results.paths = intersect(list.files(path = "Data_Clean", pattern = "baitfireoptimisationresults_transectscale_abundances_s", full = TRUE),
                          list.files(path = "Data_Clean", pattern = "_sM", full = TRUE))
results.paths = results.paths[2:4]

medsev.abundances.out = data.frame()
for (i in seq_along(results.paths)){
  t = read.csv(results.paths[i])
  medsev.abundances.out = rbind(medsev.abundances.out, t)
}

medsev.plot = abundance_plot(medsev.abundances.out)

#### Step 4c: Low severity abundance plots only 
results.paths = intersect(list.files(path = "Data_Clean", pattern = "baitfireoptimisationresults_transectscale_abundances_s", full = TRUE),
                          list.files(path = "Data_Clean", pattern = "_sL", full = TRUE))
results.paths = results.paths[2:4]

lowsev.abundances.out = data.frame()
for (i in seq_along(results.paths)){
  t = read.csv(results.paths[i])
  lowsev.abundances.out = rbind(lowsev.abundances.out, t)
}

lowsev.plot = abundance_plot(lowsev.abundances.out)

cowplot::plot_grid(lowsev.plot, medsev.plot, nrow=2, labels=c("0.2 Severity", "0.5 Severity"))


```


#### Effect of severity on abundance from optimal fire ages
So if we then compare the two severity scenarios side by side (just the medians and CIs) we can see that fire severity might have a small effect on the abundance of some of the species, reflecting the coefficients from the abundance model. This effect gets obscured a bit by the influence of different fire age distributions though, especially when we plot the entire uncertainty. 

```{r echo=FALSE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, paged.print=FALSE}
facet.labs =  data.frame(Scenario = c("s_bL_sL", "s_bA_sL","s_bAG_sL"),
                         ScenarioLab = c("Low", "Medium", "High"))

low.plot = lowsev.abundances.out %>% filter(summary=="overall") %>%
  left_join(facet.labs, by="Scenario") %>%
  mutate(ScenarioLab = factor(ScenarioLab, levels = c("Low", "Medium", "High")), Sev = "0.2")


facet.labs =  data.frame(Scenario = c("s_bL_sH", "s_bA_sH","s_bAG_sH"),
                         ScenarioLab = c("Low", "Medium", "High"))

high.plot = highsev.abundances.out %>% filter(summary=="overall") %>%
  left_join(facet.labs, by="Scenario") %>%
  mutate(ScenarioLab = factor(ScenarioLab, levels = c("Low", "Medium", "High")), Sev = "0.8")

sev.compare = rbind(low.plot, high.plot)

sev.abundance.plot.quantiles = sev.compare %>% 
  filter(summary=="overall") %>%
  group_by(ScenarioLab, Species, Sev) %>% summarise(Median = quantile(absolute_held, probs=0.5),
                                               Mean = mean(absolute_held),
                                               LCI = quantile(absolute_held, probs=0.1),
                                               UCI = quantile(absolute_held, probs=0.9))


ggplot() +
  #geom_jitter(aes(x=ScenarioLab, y = absolute_held, color=ScenarioLab),alpha=0.4) + 
  #ylim(c(0,100000)) +
  geom_pointrange(data = sev.abundance.plot.quantiles, 
                  aes(x=ScenarioLab, 
                      y=Mean, 
                      ymin=LCI, 
                      ymax=UCI, 
                      colour=Sev), position = position_dodge(width=0.5)) +
  facet_wrap(~Species, nrow=2, scales="free_y") +
  theme_cowplot() + scale_color_viridis_d(begin=0.2) + 
  ylab("Abundance") + xlab("") #+ theme(legend.position="none")


```


## Spatial Variation in Optimal Age Distribution

Now to how that all plays out spatially. This is important because we know, based on the detections, different species hang out in different locations. This will influence what the optimal fire age distribution is at each transect. 
The below plot is just for the 0.5 fire severity scenario. 

There's some important things to take note of here. Where Numbat and Woylie abundance is generally higher (e.g. Dwalgan, Balban), the relative importance of recently burnt veg is higher especially under high baiting intensity scenarios. This is what we'd expect from the model. So, i think we can be fairly comfortable that the optimisation is reflecting what is in the abundance model. 

```{r echo=FALSE, fig.height=8, fig.width=12, message=FALSE, warning=FALSE, paged.print=FALSE}
transect.data = intersect(list.files(path = "Data_Clean", pattern = "baitfireoptimisationresults_transectscale_outcomes_", full = TRUE),
                          list.files(path = "Data_Clean", pattern = "_sM", full = TRUE))
transect.data  = transect.data[2:4]
transect.data 

medsev.transects.out = data.frame()
for (i in seq_along(transect.data)){
  t = read.csv(transect.data[i])
  medsev.transects.out = rbind(medsev.transects.out, t)
}


facet.labs =  data.frame(Scenario = c("s_bL_sM", "s_bA_sM","s_bAG_sM"),
                         ScenarioLab = c("Low", "Medium", "High"))

# First we need to summarise to TSFCAT level by summing props across tsf vals, per iteration
transects.summary = medsev.transects.out %>% group_by(.id, Site, TSFCAT, Scenario) %>% summarise(prop_landscape = sum(prop_landscape)) 

# Then we want the mean prop landscape across iterations - this gives the mean proportion of the landscape chosen and CIs
plot.data = transects.summary %>% group_by(Site, TSFCAT, Scenario) %>% summarise(mean_prop_landscape=mean(prop_landscape),
                                                                                         LCI = quantile(prop_landscape, probs = 0.1),
                                                                                         UCI = quantile(prop_landscape, probs = 0.9)) %>%
  # Then add some plotting labels to make the plots nice
  left_join(facet.labs, by="Scenario") %>%
  mutate(ScenarioLab = factor(ScenarioLab, levels = c("Low", "Medium", "High"))) %>%
  mutate(TSFCATlab = gsub(" years", "", TSFCAT)) %>%
  mutate(TSFCATlab = factor(TSFCATlab, levels = c("0-5", "6-10", "11-15", "16-24", ">24")))

big.plot = plot.data %>% ggplot() + 
  geom_pointrange(aes(x=TSFCATlab, y=mean_prop_landscape, ymin =LCI, ymax = UCI, colour = ScenarioLab), position = position_dodge(width = 0.5)) +
  theme_cowplot() + scale_color_viridis_d() + 
  ylab("Proportion of Landscape") + xlab("Time Since Fire") + facet_wrap(~Site, ncol = 3) + labs(color = "Bait Intensity")
big.plot

```

# Conclusions

So, our abundance model tells us that: 

- Baiting intensity has a positive effect on almost everything (except foxes). 
- Woylie and numbat prefer recently burnt, especially when baiting intensity is high. 
- Quenda and Chuditch might prefer long unburnt, but high uncertainty. Chuditch at least prefer middle ages (5-15 years post-fire)


Our optimisation model tells us that:

- The relative importance of long unburnt increases when fox baiting is highest, but the mid ages still collectively the most optimal.
- Fox baiting does a lot of the heavy lifting. 
- Uncertainty is greatest at high time since fires. 
- There's some considerable spatial variation in the results and these generally reflect where different species hang out. 
- Based on previous versions of this, the results are pretty sensitive to which species are included (i.e. Koomal, Tammar being removed), as you would expect. So it may be worth doing sensitivity analysis on how the results change based on which species are included. 
